\begin{IEEEbiography}{Darren Cofer}{\,}is a Fellow at Collins Aerospace. His research interests include formal methods and tools for verification and certification of high-integrity systems. He received his PhD in Electrical and Computer Engineering from the University of Texas at Austin and is a senior member of the IEEE. Contact him at cofer@ieee.org.
\end{IEEEbiography}

\begin{IEEEbiography}{Isaac Amundson}{\,}is a research engineer at Collins Aerospace, focusing on MBSE, formal verification and assurance.  He received his PhD in Computer Science from Vanderbilt University.
\end{IEEEbiography}

\begin{IEEEbiography}{Junaid Babar}{\,}is a researcher at Collins Aerospace.
Do not fold, spindle, or mutilate.  
\end{IEEEbiography}

\begin{IEEEbiography}{David Hardin}{\,}is a research engineer
  at Collins Aerospace, and has made contributions in
  the areas of formal methods, high-assurance computer architecture,
  and real-time embedded Java.  He is editor of the book \emph{Design
    and Verification of Microprocessor Systems for High-Assurance
    Applications}.  He received a PhD in Electrical and Computer
  Engineering from Kansas State University.
\end{IEEEbiography}

\begin{IEEEbiography}{Konrad Slind}{\,} (PhD, TU Munich) is an industrial logician at Collins Aerospace.
  His research interests include design and implementation of higher
  order logic theorem provers, verified compilation, and
  self-describing data formats.
\end{IEEEbiography}

\begin{IEEEbiography}{Perry Alexander}{\,}is the AT\&T Foundation
  Distinguished Professor and Director of The Information and
  Telecommunication Technology Center at The University of Kansas.
  His research interests include trusted computing, remote
  attestation, formal verification and formal synthesis. He received
  his PhD from The University of Kansas.
\end{IEEEbiography}

\begin{IEEEbiography}{John Hatcliff}{\,}
John Hatcliff is a University Distinguished Professor and
Lucas-Rathbone Professor of Engineering in the Computer Science
Department at Kansas State University.  His research interests include
software architecture, formal verification, and interoperability in 
the avionics, automotive, and medical domains.
He received his PhD in Computer Science from Kansas State University.
\end{IEEEbiography}

\begin{IEEEbiography}{Robby}{\,}
is a Professor of Computer Science at Kansas State University working
in the area of formal methods, software engineering, and programming
languages.
%%He received his PhD in Computer Science from Kansas State University.
He received a NASA Turning Goals Into Reality award in 2003,
a NSF CAREER award in 2007, an ICSE 2000 Most Influential Paper award in 2010,
and an ACM SIGSOFT Impact award in 2010.
\end{IEEEbiography}

\begin{IEEEbiography}{Gerwin Klein}{\,}
is Chief Scientist at Proofcraft and Conjoint Professor at UNSW Sydney. His
research interests include software verification, semantics of programming
languages, and proof engineering. He is the architect of the seL4 microkernel
verification which received the SIGOPS Hall of Fame Award. He received his PhD
in Computer Science from TU Munich.
\end{IEEEbiography}

\begin{IEEEbiography}{Corey Lewis}{\,}%
  is a Senior Proof Engineer at UNSW Sydney. He has been involved in all stages
  of the verification of the seL4 microkernel.
\end{IEEEbiography}

\begin{IEEEbiography}{Eric Mercer}{\,}
  is an Associate Professor at Brigham Young University.
  His research interests include software verification, model checking, static analysis, and programming languages.
  He received his PhD in Electrical Engineering from the University of Utah.
\end{IEEEbiography}

\begin{IEEEbiography}{John Shackleton}{\,}
  is a Senior Principal Research Scientist at Adventium Labs,
  focused on real-time embedded systems, cybersecurity, and
  model-based system engineering and analysis.
\end{IEEEbiography}

%Author's latest degree received or which he/she is currently pursuing
%(He received the B.S. degree and the M.S. degree...."). Author's
%research interest. Association with any official journals or
%conferences; major professional and/or academic achievements, i.e.,
%best paper awards, research grants, etc.; any publication information
%(number of papers and titles of books published). Author membership
%information, e.g., is a member of the IEEE and the IEEE Computer
%Society, if applicable, is noted at the end of the
%biography. Biography is limited to single paragraph only (He is a
%member of IEEE, etc.). All biographies should be limited to one
%paragraph, five to six sentences
