\documentclass{IEEEcsmag}

\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}

\usepackage{upmath}

\jvol{XX}
\jnum{XX}
\paper{8}
\jmonth{May/June}
\jname{Security \& Privacy}
\pubyear{2019}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\setcounter{secnumdepth}{0}

\begin{document}

\sptitle{Department: Head}
\editor{Editor: Name, xxxx@email}

\title{Cyber Assured Systems Engineering at Scale}

\author{Darren Cofer, Isaac Amundson, Junaid Babar, David Hardin, Konrad Slind}
\affil{Collins Aerospace}

\author{S. B. Author, Jr.}
\affil{Second Affiliation}

\author{T. C. Author, III}
\affil{Third Affiliation}

\markboth{Department Head}{Paper title}

\begin{abstract}
Abstract text goes here. This single paragraph ($\le$50 words) summarizes the significant aspects of the manuscript. Often it indicates whether the manuscript is a report of new work, a review or overview, or a combination of thereof. Do not cite references in the abstract. Papers must not have been published previously, must fit into the theme of an open Call for Papers, and must be targeted toward the general technical reader. 
\end{abstract}

\maketitle


\chapterinitial{The introduction} should provide background information (including relevant references) and should indicate the purpose of the manuscript. Cite relevant work by others, including research outside your company. Place your work in perspective by referring to other research papers. Inclusion of statements at the end of the introduction regarding the organization of the manuscript can be helpful to the reader.

Darren, David?
\input{intro}

\section{INNOVATIONS}
Darren
\input{innovations}

\section{MOTIVATION}
Eric?
\input{motivation}

\section{BRIEFCASE WORK FLOW}
Darren
\input{workflow}

\subsection{Requirements}
Isaac, Junaid

\subsection{Cyber Transforms}
Isaac

\subsection{High Assurance Component Synthesis}
Konrad, Eric, Junaid

\subsection{Remote Attestation}
Perry

\subsection{Compositional Analysis}
Isaac, Junaid

\subsection{Information Flow Analysis}
John H

\subsection{Real-Time Scheduling}
John S

\subsection{Infrastructure Code Generation}
John H

\subsection{Secure Microkernel}
Corey

\subsection{Assurance Case}
Isaac

\section{AIRCRAFT APPLICATION}
David, Darren?

Describe how we have used the BriefCASE tools to add new functionality to the CAAS architecture.  

\section{CONCLUSION}

The manuscript should include a conclusion. In this section, summarize what was described in your paper. Future directions may also be included in this section. Authors are strongly encouraged not to reference multiple figures or tables in the conclusion; these should be referenced in the body of the paper.

\section{ACKNOWLEDGMENT}

This work was funded by DARPA contract HR00111890001. The
views, opinions and/or findings expressed are those of the author
and should not be interpreted as representing the official views or
policies of the Department of Defense or the U.S. Government.


\begin{thebibliography}{1}

\bibitem{AA1}
G. M. Amdahl, G. A. Blaauw, and F. P. Brooks, ``Architecture of the IBM System/360,'' {\it IBM J. Res. \& Dev}., vol. 8, no. 2, pp. 87--101, 1964. (journal)

\bibitem{BB1}
IBM Corporation, IBM Knowledge Center - IBM Secure Service Container (Secure Service Container). [Online]. Available: {https://www.ibm.com/support/\break knowledgecenter/en/HW11R/com.ibm.hwmca.kc\_se.doc/\break introductiontotheconsole/wn2131zaci.html} (URL)

\bibitem{CC1}
J. Williams, ``Narrow-band analyzer,'' PhD dissertation, Dept. of Electrical Eng., Harvard Univ., Cambridge, MA: 1993. (Thesis or dissertation)

\bibitem{DD1}
J. M. P. Martinez, R. B. Llavori, M. J. A. Cabo, et al., ``Integrating data warehouses with web data: A survey,'' {\it IEEE Trans. Knowledge and Data Eng}., preprint, Dec. 21, 2007, doi:10.1109/TKDE.2007.190746. (PrePrint)

\bibitem{EE1}
W.-K. Chen, {\it Linear Networks and Systems}, Belmont, CA: Wadsworth, pp. 123--135, 1993. (book)

\bibitem{FF1}
S. P. Bingulac, ``On the compatibility of adaptive controllers,'' {\it Proc. Fourth Ann. Allerton Conf. Circuits and Systems Theory}, pp. 8--16, 1994. (conference proceedings)\vadjust{\vfill\pagebreak}

\bibitem{GG1}
K. Elissa, ``An overview of decision theory,'' unpublished. (Unpublished manuscript)

\bibitem{HH1}
R. Nicole, ``The last word on decision theory,'' {\it J. Computer Vision}, submitted for publication. (Pending publication)

\bibitem{II1}
C. J. Smith and J. S. Smith, Rocky Mountain Research Laboratories, Boulder, CO, personal communication, 1992. (Personal communication)
\end{thebibliography}


\begin{IEEEbiography}{First A. Author}{\,}current employment (is
currently with XYZ Corporation, New York, NY, USA). Author's latest degree received or which he/she is currently pursuing (He received the B.S. degree and the M.S. degree...."). Author's research interest. Association with any official journals or conferences; major professional and/or academic achievements, i.e., best paper awards, research grants, etc.; any publication information (number of papers and titles of books published). Author membership information, e.g., is a member of the IEEE and the IEEE Computer Society, if applicable, is noted at the end of the biography. Biography is limited to single paragraph only (He is a member of IEEE, etc.). All biographies should be limited to one paragraph, five to six sentences, consisting of the following: (e.g., ``Dr. Author received a B.S. degree and an M.S. degree $\ldots$.''), including years achieved; association with any official journals or conferences; major professional and/or academic achievements, i.e., best paper awards, research grants, etc.; any publication information (number of papers and titles of books published); current research interests; association with any professional associations. Author membership information, e.g., is a member of the IEEE and the IEEE Computer Society, if applicable, is noted at the end of the biography. Contact him/her at faauthor@xyz.com.
\end{IEEEbiography}

\begin{IEEEbiography}{Second B. Author, Jr.,}{\,}is with ABC Corporation, Bblingen, Germany. Ms. Author's biography appears here.  Contact him/her at sbauthor@abc.com.
\end{IEEEbiography}

\begin{IEEEbiography}{Third C. Author, III,}{\,}is with DEF Corporation, Tokyo, Japan. Dr. Author's biography appears here.  Contact him/her at tcauthor@def.com.
\end{IEEEbiography}

\end{document}

