The correctness of the high-assurance components inserted
by \briefcase \ transformations means that each such component
must meet its \agree{} contract. This obligation is addressed by
\emph{formal synthesis}, using the Semantic Properties of Language
and Automata Theory (\splat) tool.  Given a sufficiently detailed formal
specification of component behavior, \splat{} generates code,
as well as proofs showing that the generated code is
correctly compiled and meets its specification \cite{case-models-2021}.

The formal languages that filters, gates, and monitors are generated
from include regular expressions, contiguity types, and Lustre.
For each of these languages, we have infrastructure
%(see Figure \ref{fig:synthesis})
that (a) translates formal specifications to code and (b) proves the
correctness of the translation using the HOL4 theorem proving system.
%\cite{hol4:overview}.
The generated code is \emph{CakeML}, a dialect of Standard ML
%\cite{SML97}
possessing a fully verified compiler \cite{cakeml}.

%\begin{figure}[h]
%\begin{center}
%\begin{tikzpicture}[scale = 0.7]
%\node (A) at (0,2) [shape=rectangle,draw]{\textit{Regexp}};
%\node (B) at (0,0) [shape=rectangle,draw]{\textit{Contig type}};
%\node (C) at (0,-2) [shape=rectangle,draw]{\textit{Lustre}};
%\node (D) at (4,0) [shape=rectangle,draw]{\textit{CakeML}};
%\node (E) at (8,0) [shape=rectangle,draw]{\textit{Binary}};
%\draw [->,thick] (A) to (D);
%\draw [->,thick] (B) to (D);
%\draw [->,thick] (C) to (D);
%\draw [->,thick] (D) to (E);
%\end{tikzpicture}
%\end{center}
%\caption{\splat{} Verified Synthesis Path.\label{fig:synthesis}}
%\end{figure}

Regular expressions and contiguity types are formalisms well-suited
for expressing classes of constraints on the data passed in
messages. Thus, they provide a useful basis for expressing
filters. Regular expressions compile to efficient finite state
automata, generating a correctness proof along the way.
%\cite{case-verified-filter}.
We have also synthesized regular
expressions to hardware using this proof-producing
technique.
% \cite{formal-filter-synth-langsec}.
Contiguity types can capture more complex
data formats, including variable-length arrays and union structures
which are used in the Mission Planner found in our UAV example.
%this level of expressiveness was needed to handle the messages of UxAS.
We deploy a verified contiguity-type based parser generator
%\cite{contiguity-types}
to decode and check that the serialized message data is well-formed
relative to its specification.

Gates and monitors can require arbitrarily complex computations for
their work; hence we also support code generation from Lustre. We have
formalized the semantics of Lustre and are using it as the basis for a
formal translation to CakeML.

Since code generated from \splat{} is deployed as a scheduled thread
in a real-time environment, there are two aspects to consider: (1)
correctness of a `one shot` thread execution (discussed above), and
(2) correctness of the perpetual re-execution of the thread.
Modeling the latter and proving relevant properties is discussed in
\cite{johannes:repeat}.
